---
title: "Final presentation of state-space extraction of the time series of diseases"
author: "D. Erik Boonstra, MS and Joe E. Cavanaugh, PhD"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: TRUE
---

```{r setup, include = FALSE}
R <- list.files(path = "./R", pattern = "*.R", full.names = TRUE)
sapply(R, source, .GlobalEnv)
library(knitr)
library(kableExtra)
```

```{r resultsdata, include = FALSE}
load("./outputs/ss-series/inoutpatient_extract.RData")
load("./outputs/ss-series/clustering.RData")
load("./outputs/ss-series/causation_mods.RData")
change <- readRDS(file = "./outputs/ss-series/incidence_change.rds")
```

# Purpose
Identify diseases that have the same seasonality as influenza, which will allow relations to be established between influenza and the diseases. The primary goal is to determined if obtaining the current variant of influenza vaccine will reduce the incidence rate of diseases seasonally realted to influenza.

# Results

An analytical approach was devised to estimate the change in incidence for diseases that are seasonally related to influenza. The approach is outlined as we go through this document. The results on this analysis is based on records from 2003 through 2013 based on the ICD-9-CM coding system and included all inpatient and outpatient records.

## Splitting of series 
First, for each disease under consideration, at this moment in time, had their observed incidence series extracted into trend, seasonal, and anomaly + error components (i.e., state-space modeling) based on Kalman filtering and smoothing. This extraction of series borrowed from the work of fourth edition of Shumway and Stoffer's *Time Series Analysis and Its Applications With R Examples* and Tang and Cavanaugh (2015). The trend component was modeled with a random walk process, while it was assumed the seasonal component is expected to sum to zero over a complete period or 12 months.

### Influenza
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = flu_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

### Other diseases {.tabset .tabset-fade}
Considering influenza peaks in the winter months (December, Janudary, February, and March), we are looking for other diseases that also peak in these months. The decomposition of the disease series below are organized by their seasonality (winter, summer, and no seasonality).

#### Winter seasonality {.tabset .tabset-fade .tabset-pills}

##### Bronchitis
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = bronchitis_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Upper respiratory infections
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = up_resp_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Pneumonia
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = pneumonia_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Viral infections
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = viral_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Infection of eye
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = eye_infct_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Otitis media
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = otitis_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Nonspecific chest pain
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = chest_pain_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Tonsillitis
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = tonsillitis_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

#### Summer seasonality {.tabset .tabset-fade .tabset-pills}

##### Cancer of breast
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = cancerbreast_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Meningitis
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = meningitis_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Other infections
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = other_infct_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Other ear and sense organ disorders
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = other_ear_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Varicoses veins of lower extremity
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = varicoses_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Other diseases of veins and lymphatics
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = other_veins_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

#### No seasonality {.tabset .tabset-fade .tabset-pills}

##### Gout
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = gout_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Liveborn
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = liveborn_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### Encephalitis
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = encephalitis_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

##### AMI
The current population does not characterize the seasonality of AMI appropriately. A cohort focused on older individuals would be necessary to see the seasonality of AMI.
```{r, echo = FALSE, out.width = "100%"}
signal_extract_plot(
  data = ami_inout_extract,
  ylab = "Standardized log(Incidence per 100,000)"
)
```

## Clustering of diseases

With the disease series decomposed into their trend, seasonal, and anomaly + error components, we can being determining which diseases are seasonally related to the influenza. We imployed a simply correlation based clustering algorithm to determine which diseases are related to influenza.

### Global (Seasonal) clustering {.tabset .tabset-fade .tabset-pills}
The first step in the clustering algorithm is to determine which seasonal components of the diseases are highly correlated with the seasonal component of influenza. We set the correlation filtering threshold at +0.7 to define "highly correlated".
```{r, echo = FALSE, out.width = "100%"}
ylim <- c(0, 5)
graphics::hist(
  x = corr_inout$rho_ssm, xlim = c(-1, 1), ylim = ylim,
  breaks = seq(-1, 1, by = 0.1),
  xlab = expression(rho), main = "",
  col = "gray", border = "white"
)
graphics::abline(v = 0.7, col = "firebrick", lty = 3, lwd = 2)
boonstra::legend_top(
  legend = expression(rho == 0.7), col = "firebrick", lty = 3, lwd = 2
)

corr_inout <- corr_inout[order(corr_inout$rho_ssm,  decreasing = TRUE), ]
corr_inout$ssm_cluster <- ifelse(
  test = corr_inout$disease %in% corr_inout_ssm$disease,
  yes = "**",
  no = ""
)
row.names(corr_inout) <- NULL
tab <- knitr::kable(
  x = subset(corr_inout, select = c(disease, rho_ssm, ssm_cluster)),
  digits = 4, align = c("l", "r", "l"),
  col.names = c(
    "Diseases", "Global correlation", "Global cluster"
  )
)
kableExtra::kable_styling(kable_input = tab)
```

#### Pneumonia
```{r, echo = FALSE, out.width = "100%"}
graphics::plot(
  x = c(flu_inout_extract$ssm),
  y = c(pneumonia_inout_extract$ssm),
  xlab = "Flu", ylab = "Pneumonia",
  main = "Seasonal trends",
  type = "p", pch = 16
)
abline(h = 0, col = "red", lty = 3)
```

#### Bronchitis
```{r, echo = FALSE, out.width = "100%"}
graphics::plot(
  x = c(flu_inout_extract$ssm),
  y = c(bronchitis_inout_extract$ssm),
  xlab = "Flu", ylab = "Bronchitis",
  main = "Seasonal trends",
  type = "p", pch = 16
)
abline(h = 0, col = "red", lty = 3)
```

#### Upper respiratory infections
```{r, echo = FALSE, out.width = "100%"}
graphics::plot(
  x = c(flu_inout_extract$ssm),
  y = c(up_resp_inout_extract$ssm),
  xlab = "Flu", ylab = "Upper respiratory infections",
  main = "Seasonal trends",
  type = "p", pch = 16
)
abline(h = 0, col = "red", lty = 3)
```

#### Otitis media
```{r, echo = FALSE, out.width = "100%"}
graphics::plot(
  x = c(flu_inout_extract$ssm),
  y = c(otitis_inout_extract$ssm),
  xlab = "Flu", ylab = "Otitis media",
  main = "Seasonal trends",
  type = "p", pch = 16
)
abline(h = 0, col = "red", lty = 3)
```

#### Viral infections
```{r, echo = FALSE, out.width = "100%"}
graphics::plot(
  x = c(flu_inout_extract$ssm),
  y = c(viral_inout_extract$ssm),
  xlab = "Flu", ylab = "Viral infections",
  main = "Seasonal trends",
  type = "p", pch = 16
)
abline(h = 0, col = "red", lty = 3)
```

#### Tonsillitis
```{r, echo = FALSE, out.width = "100%"}
graphics::plot(
  x = c(flu_inout_extract$ssm),
  y = c(tonsillitis_inout_extract$ssm),
  xlab = "Flu", ylab = "Tonsillitis",
  main = "Seasonal trends",
  type = "p", pch = 16
)
abline(h = 0, col = "red", lty = 3)
```

### Local (Anomaly + error) clustering
Of the diseases that have a seasonal component that is "highly correlated" correlated with the seasonal component of influenza, they are examined to see if their anomaly + error component is also correlated with anomaly + error component of influenza. This examination of the anomaly + error components allows us to determine relations between the diseases once the trend and seasonal components have be stripped away. The correlation threshold for this examination is set to +0.2.
```{r, echo = FALSE, out.width = "100%"}
graphics::hist(
  x = corr_inout$rho_asm, xlim = c(-1, 1), ylim = ylim,
  breaks = seq(-1, 1, by = 0.1),
  xlab = expression(rho), main = "",
  col = "gray", border = "white"
)
graphics::abline(v = 0.2, col = "firebrick", lty = 3, lwd = 2)
boonstra::legend_top(
  legend = expression(rho == 0.2), col = "firebrick", lty = 3, lwd = 2
)

corr_inout <- corr_inout[order(corr_inout$rho_asm,  decreasing = TRUE), ] #nolint
corr_inout$asm_cluster <- ifelse(
  test = corr_inout$disease %in% corr_inout_asm$disease,
  yes = "***",
  no = ""
)
row.names(corr_inout) <- NULL
tab <- knitr::kable(
  x = subset(
    x = corr_inout,
    select = c(disease, rho_asm, ssm_cluster, asm_cluster)
  ),
  digits = 4, align = c("l", "r", "l", "l"),
  col.names = c(
    "Diseases", "Local correlation", "Global cluster",
    "Local cluster"
  )
)
kableExtra::kable_styling(kable_input = tab)
```

## Effects of influenza
Finally, the diseases that are globally and locally clustered with influenza are further examined for causation between the diseases and influenza. Simple linear regression models are first constructed for these diseases, where the response variable is the sum of the seasonal and anomaly + error components of the disease of interest and the predictor variable is the sum of the seasonal and anomaly + error components of influenza. While not reported in this document, the effect of influenza on each of these diseases is statistically significant at a trivial 0.05 significance level. Using these linear models, we can estimate the change in mean incidence for each disease during the winter months given we reduce the influenza maximum mean incidence by 20% during these months.
```{r, echo = FALSE}
change <- change[order(change$raw_change, decreasing = TRUE), ]
change$relative_change <- change$relative_change * 100
row.names(change) <- NULL
tab <- knitr::kable(
  x = change,
  digits = 4, align = c("l", "r", "r"),
  col.names = c(
    "Disease", "Raw change in incidence per 100,000 cases",
    "Relative (%) change in incidence per 100,000 cases"
  )
)
kableExtra::kable_styling(kable_input = tab)
```